TGI Spinal Analysis Code

### 2023-01-04 analysis/tgi-spinal_analysis.Rmd
completed marginal effect plots

# plotting - within
ggplot(data = cold_eff %>% 
         filter(facet == 'within'), 
       aes(label, predicted, group = group, colour = group),) +
  geom_point(position = position_dodge(.3)) +
  geom_line(position = position_dodge(.3)) +
  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
                position = position_dodge(.3), width = .1) +
  ylim(0.1, 0.5) +
  theme_bw()
# plotting - across
ggplot(data = cold_eff %>% 
         filter(facet == 'across'), 
       aes(label, predicted, group = group, colour = group),) +
  geom_point(position = position_dodge(.3)) +
  geom_line(position = position_dodge(.3)) +
  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
                position = position_dodge(.3), width = .1) +
  ylim(0.1, 0.5) +
  theme_bw() +
  theme(legend.title = element_blank())
```

@@

Anova(model.warm)

eff <- ggeffects::ggeffect(model.warm, terms = c('cold_cond','condition'),
                           type = 'random', ci.lvl = .95)
plot(eff)
```

# Burn
The burning hypothesis is only for participants that experience burning TGI 
(aka are responders)
```{r burnmod}
# First, remove non-responders
df_resp <- df_long %>% 
  filter(responder == 1)
# check n
n <- count(df_resp, 'ID')
length(n$ID)
# Try and model all with ratings
model.burn = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + 
                                trial_n + (1|ID) + (1|order),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_resp %>% filter(quality == 'burn'),
                      na.action = na.omit) 
mb <- summary(model.burn)
mb

Anova(model.burn)

# Zero inflation marginal effects plot of all models
```{r zero_plots}
# Getting the marginal effects for plotting
# First the zeros - create new lm mo
df_long$bin <- ifelse(df_long$VAS == 0, 1, 0)

# model for each VAS
cold.eff <- glm(bin~1+manipulation, 
                  family = binomial(link = 'logit'),
                  data = df_long %>% filter(quality == 'cold'))
summary(cold.eff)

# Data-frames
cold_zeff <- ggeffects::ggeffect(cold.eff, terms = c('manipulation'))
# changing labels for plotting
cold_zeff$x <- factor(cold_zeff$x, labels = c('Non-TGI', 'TGI'))

# plotting
ggplot(cold_zeff, aes(x, predicted)) +
  geom_point() +
  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
                width = .1) +
  theme_bw()

# Run model checks on all
```{r checks, warning=FALSE}
# cold assumption - on n = 50
mc.assump <- simulateResiduals(model.cold, n = 1000)
plot(mc.assump)
# warm assumption - on n = 50
mw.assump <- simulateResiduals(model.warm, n = 1000)
plot(mw.assump)
# warm assumption - on n = 50
mb.assump <- simulateResiduals(model.burn, n = 1000)
plot(mb.assump)
```
# EXPLORATORY HYPOTHESES
# Correlation between quality (cold/warm/burn)

>>>>

# plotting - within
ggplot(data = cold_eff %>% 
         filter(facet == 'within'), 
       aes(label, predicted, group = group, colour = group),) +
  geom_point(position = position_dodge(.3), size = 2.5) +
  geom_line(position = position_dodge(.3), size = 1) +
  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
                position = position_dodge(.3), width = .1, size = .8) +
  ylim(0, 0.5) +
  labs(x = NULL, y = 'Predicted Cold Rating (0 - 1)') +
  facet_wrap(~facet) +
  scale_colour_manual(values = c(blue[4], blue[7])) +
  theme_classic() +
  theme(legend.title = element_blank(),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12),
        strip.text = element_text(size = 12),
        legend.text = element_text(size = 11)) -> plot_coldw_eff
# plotting - across
ggplot(data = cold_eff %>% 
         filter(facet == 'across'), 
       aes(label, predicted, group = group, colour = group),) +
  geom_point(position = position_dodge(.3), size = 2.5) +
  geom_line(position = position_dodge(.3), size = 1) +
  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
                position = position_dodge(.3), width = .1, size = .8) +
  ylim(0, 0.5) +
  labs(x = NULL, y = '') +
  facet_wrap(~facet) +
  scale_colour_manual(values = c(blue[4], blue[7])) +
  theme_classic() +
  theme(legend.title = element_blank(),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12),
        strip.text = element_text(size = 12),
        legend.text = element_text(size = 10)) -> plot_colda_eff

# combine
plot_cold_eff1 <- ggarrange(plot_coldw_eff, plot_colda_eff,
                           ncol = 2, nrow = 1,
                           common.legend = TRUE,
                           legend = 'right')
plot_cold_eff1
```

@@

Anova(model.warm)
```
# Marginal effect plots of full model - warm
```{r}
warm_eff <- ggeffects::ggpredict(model.warm, terms = c('cold_cond', 'manipulation', 'condition'),
                            ci.lvl = .95)
# changing labels for plotting
warm_eff$group <- factor(warm_eff$group, labels = c('Non-TGI', 'TGI'))
warm_eff <- warm_eff %>% 
  mutate(label = 
           case_when(facet == 'across' & x == 'prox_caud' ~ 'caudal',
                     facet == 'across' & x == 'dist_rostr' ~ 'rostral',
                     facet == 'within' & x == 'prox_caud' ~ 'proximal',
                     facet == 'within' & x == 'dist_rostr' ~ 'distal',) 
         )

warm_eff$label = factor(warm_eff$label, levels = c('proximal','distal','caudal','rostral'))

# plotting - within
ggplot(data = warm_eff %>% 
         filter(facet == 'within'), 
       aes(label, predicted, group = group, colour = group),) +
  geom_point(position = position_dodge(.3), size = 2.5) +
  geom_line(position = position_dodge(.3), size = 1) +
  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
                position = position_dodge(.3), width = .1, size = .8) +
  ylim(0, 0.5) +
  labs(x = NULL, y = 'Predicted Warm Rating (0 - 1)') +
  facet_wrap(~facet) +
  scale_colour_manual(values = c(oran[4], oran[7])) +
  theme_classic() +
  theme(legend.title = element_blank(),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12),
        strip.text = element_text(size = 12),
        legend.text = element_text(size = 11)) -> plot_warmw_eff
# plotting - across
ggplot(data = warm_eff %>% 
         filter(facet == 'across'), 
       aes(label, predicted, group = group, colour = group),) +
  geom_point(position = position_dodge(.3), size = 2.5) +
  geom_line(position = position_dodge(.3), size = 1) +
  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
                position = position_dodge(.3), width = .1, size = .8) +
  ylim(0, 0.5) +
  labs(x = NULL, y = '') +
  facet_wrap(~facet) +
  scale_colour_manual(values = c(oran[4], oran[7])) +
  theme_classic() +
  theme(legend.title = element_blank(),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12),
        strip.text = element_text(size = 12),
        legend.text = element_text(size = 10)) -> plot_warma_eff

# combine
plot_warm_eff1 <- ggarrange(plot_warmw_eff, plot_warma_eff,
                           ncol = 2, nrow = 1,
                           common.legend = TRUE,
                           legend = 'right')
plot_warm_eff1
```
# Burn
The burning hypothesis is only for participants that experience burning TGI 
(aka are responders)
```{r burnmod}
# First, remove non-responders
df_resp <- df_long %>% 
  filter(responder == 1)
# check n
n <- count(df_resp, 'ID')
length(n$ID)
# Try and model all with ratings
model.burn = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + 
                                trial_n + (1|ID) + (1|order),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_resp %>% filter(quality == 'burn'),
                      na.action = na.omit) 
mb <- summary(model.burn)
mb

Anova(model.burn)
```

# Marginal effect plots of full model - burn
```{r}
burn_eff <- ggeffects::ggpredict(model.burn, terms = c('cold_cond', 'manipulation', 'condition'),
                            ci.lvl = .95)
# changing labels for plotting
burn_eff$group <- factor(burn_eff$group, labels = c('Non-TGI', 'TGI'))
burn_eff <- burn_eff %>% 
  mutate(label = 
           case_when(facet == 'across' & x == 'prox_caud' ~ 'caudal',
                     facet == 'across' & x == 'dist_rostr' ~ 'rostral',
                     facet == 'within' & x == 'prox_caud' ~ 'proximal',
                     facet == 'within' & x == 'dist_rostr' ~ 'distal',) 
         )

burn_eff$label = factor(burn_eff$label, levels = c('proximal','distal','caudal','rostral'))

# plotting - within
ggplot(data = burn_eff %>% 
         filter(facet == 'within'), 
       aes(label, predicted, group = group, colour = group),) +
  geom_point(position = position_dodge(.3), size = 2.5) +
  geom_line(position = position_dodge(.3), size = 1) +
  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
                position = position_dodge(.3), width = .1, size = .8) +
  ylim(0, 0.5) +
  labs(x = NULL, y = 'Predicted Burn Rating (0 - 1)') +
  facet_wrap(~facet) +
  scale_colour_manual(values = c(purp[4], purp[7])) +
  theme_classic() +
  theme(legend.title = element_blank(),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12),
        strip.text = element_text(size = 12),
        legend.text = element_text(size = 11)) -> plot_burnw_eff
# plotting - across
ggplot(data = burn_eff %>% 
         filter(facet == 'across'), 
       aes(label, predicted, group = group, colour = group),) +
  geom_point(position = position_dodge(.3), size = 2.5) +
  geom_line(position = position_dodge(.3), size = 1) +
  geom_errorbar(aes(label, ymin = conf.low, ymax = conf.high),
                position = position_dodge(.3), width = .1, size = .8) +
  ylim(0, 0.5) +
  labs(x = NULL, y = '') +
  facet_wrap(~facet) +
  scale_colour_manual(values = c(purp[4], purp[7])) +
  theme_classic() +
  theme(legend.title = element_blank(),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12),
        strip.text = element_text(size = 12),
        legend.text = element_text(size = 10)) -> plot_burna_eff

# combine
plot_burn_eff1 <- ggarrange(plot_burnw_eff, plot_burna_eff,
                           ncol = 2, nrow = 1,
                           common.legend = TRUE,
                           legend = 'right')
plot_burn_eff1
```

# Zero inflation marginal effects plot of all models
```{r zero_plots}
# Getting the marginal effects for plotting
# First the zeros - create new lm mo
df_long$bin <- ifelse(df_long$VAS == 0, 1, 0)
df_resp$bin <- ifelse(df_resp$VAS == 0, 1, 0)

# model for each VAS
# cold
cold.zeff <- glm(bin~1+manipulation, 
                  family = binomial(link = 'logit'),
                  data = df_long %>% filter(quality == 'cold'))
summary(cold.zeff)
# warm
warm.zeff <- glm(bin~1+manipulation, 
                  family = binomial(link = 'logit'),
                  data = df_long %>% filter(quality == 'warm'))
summary(warm.zeff)
# burn
burn.zeff <- glm(bin~1+manipulation, 
                  family = binomial(link = 'logit'),
                  data = df_resp %>% filter(quality == 'burn'))
summary(burn.zeff)

# Data-frames
cold_zeff <- ggeffects::ggeffect(cold.zeff, terms = c('manipulation'))
warm_zeff <- ggeffects::ggeffect(warm.zeff, terms = c('manipulation'))
burn_zeff <- ggeffects::ggeffect(burn.zeff, terms = c('manipulation'))
# changing labels for plotting
cold_zeff$x <- factor(cold_zeff$x, labels = c('Non-TGI', 'TGI'))
warm_zeff$x <- factor(warm_zeff$x, labels = c('Non-TGI', 'TGI'))
burn_zeff$x <- factor(burn_zeff$x, labels = c('Non-TGI', 'TGI'))

# plotting - cold
ggplot(cold_zeff, aes(x, predicted, colour = x)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
                width = .05, size = .8) +
  labs(y = 'Predicted proportion of zeros', x = NULL) +
  ylim(0,.25) +
  scale_colour_manual(values = c(blue[4], blue[7])) +
  theme_classic() + 
  theme(legend.position = 'none',
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12)) -> plot_zcold

# warm
ggplot(warm_zeff, aes(x, predicted, colour = x)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
                width = .05, size = .8) +
  labs(y = 'Predicted proportion of zeros', x = NULL) +
  ylim(.45,.7) +
  scale_colour_manual(values = c(oran[4], oran[7])) +
  theme_classic() + 
  theme(legend.position = 'none',
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12)) -> plot_zwarm

# burn
ggplot(burn_zeff, aes(x, predicted, colour = x)) +
  geom_point(size = 2.5) +
  geom_errorbar(aes(x, ymin = conf.low, ymax = conf.high),
                width = .05, size = .8) +
  labs(y = 'Predicted proportion of zeros', x = NULL) +
  ylim(.05,.3) +
  scale_colour_manual(values = c(purp[4], purp[7])) +
  theme_classic() + 
  theme(legend.position = 'none',
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12)) -> plot_zburn
```

# Compile all marginal effect plots
```{r}
# Cold
plot_cold_eff <- ggarrange(plot_zcold, plot_cold_eff1,
                   ncol = 2, nrow = 1,
                   widths = c(.35,1))
# add title
plot_cold_eff <- annotate_figure(plot_cold_eff, top = text_grob("Cold Ratings", 
                                                size = 12, hjust = 4.05))
plot_cold_eff

# Warm
plot_warm_eff <- ggarrange(plot_zwarm, plot_warm_eff1,
                   ncol = 2, nrow = 1,
                   widths = c(.35,1))
# add title
plot_warm_eff <- annotate_figure(plot_warm_eff, top = text_grob("Warm Ratings", 
                                                size = 12, hjust = 3.69))
plot_warm_eff

# Burn
plot_burn_eff <- ggarrange(plot_zburn, plot_burn_eff1,
                   ncol = 2, nrow = 1,
                   widths = c(.35,1))
# add title
plot_burn_eff <- annotate_figure(plot_burn_eff, top = text_grob("Burn Ratings", 
                                                size = 12, hjust = 4.1))
plot_burn_eff

# Compile all!
plot_eff <- ggarrange(plot_cold_eff, plot_warm_eff, plot_burn_eff,
                      ncol = 1, nrow = 3)
plot_eff

ggsave('h2_effects_plot.png', plot_eff, device = NULL, path = anaPath,
       width = 9, height = 8, dpi = 600)
```
# Run model checks on all
```{r checks, warning=FALSE}
# cold assumption - on n = 50
mc.assump <- simulateResiduals(model.cold, n = 1000)
plot(mc.assump)
# warm assumption - on n = 50
mw.assump <- simulateResiduals(model.warm, n = 1000)
plot(mw.assump)
# warm assumption - on n = 50
mb.assump <- simulateResiduals(model.burn, n = 1000)
plot(mb.assump)
```
# EXPLORATORY HYPOTHESES
# Correlation between quality (cold/warm/burn)
